---
title: "jdrun0"
author: "santiago"
date: "2023-07-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r}
list.files(path="../../masterdata/data/")
readr::read_csv("../../masterdata/data/Emp_master08-02.csv")->emp_master
readr::read_csv("../../masterdata/data/JRS_recent_7_26.csv")->jrs


```

# First, identify what data from JD project can be received from jrs and what from EMP_master.

-----------------------------------------------------------------------------------------------------------------------------------------------------------------

1. Reports To :  Get the dsm from jrs, match with supervisor dsm, then match that with jrs `emp_master`
2. DSM : `key` get from jrs and JD
3. DSM title: `sap` Get from jrs
4. Exemption status: `sap` from jrs: flsa
5. Job Family: `jrs` if not `sap`:
6. Bargaining unit : *maybe from jd*
7. Pay grade level: `jrs`: (join `pay grade group` and `pay grade level` `sap` (have to join `Pay Grade` and `Pay Grade Level`)



## Display that employees under the same dsm report to supervisors with different dsm then get supervisor dsm to a dsm
```{r supervisor}
#Show that employees with same dsm report to managers
emp_master %>% select(c(Employee, `DSM Code`, `DSM Code Title`, `Current Supervisor`,`Current Supervisor Title`)) %>% 
  filter(str_detect(`DSM Code Title`, "^COMPENSATION C"))

emp_master %>% 
  filter(str_detect(`DSM Code Title`, "COMPENSATION "))
  
# Get table with dsm for all employees and who they report to. Then delete duplicates

emp_master %>% 
  select(c( supervisor_position =`Current Supervisor Position`,`DSM Code`, `Employee Position`)) %>% 
  distinct(.keep_all = T) %>% 
  mutate(supervisor_position = as.double(supervisor_position))->dsm_to_supervisor_position



dsm_to_supervisor_position[2:3] %>% 
  rename(supervisor_position =`Employee Position`, supervisor_dsm =`DSM Code` )->supervisor

dsm_to_supervisor_position[1:2] %>% 
  left_join(supervisor)->dsm_to_supervisor_dsm

#Below is final result, we have a df that matches DSM CODE key with supervisor DSM, so that we can match to other supervisor attributes.


```

```{r supervisor}
#Create supervisor title object with key for jrs
jrs %>% 
  select(c(supervisor_dsm = DSM, supervisor_title_jrs =`Job Title`))->supervisor_title_jrs

emp_master %>% 
  select(c(supervisor_dsm = `DSM Code`, supervisor_title_sap = `DSM Code Title`))->supervisor_title_sap

#match 
dsm_to_supervisor_dsm %>%
  left_join(supervisor_title_sap) %>% 
  mutate(supervisor_dsm = as.double(supervisor_dsm)) %>% 
  left_join(supervisor_title_jrs) %>% 
  relocate(`DSM Code`) %>% 
  distinct()->DSM_to_supervisor

```

join `pay grade group` and `pay grade level
```{r}
jrs %>% 
  select(c(dsm= DSM, `Job Title`, FLSA,`Job Family`,`Pay Grade Group`,Level, Certifications))->jrs_attributes

DSM_to_supervisor %>% 
  mutate(dsm= as.numeric(`DSM Code`),.before = everything()) %>% 
  left_join(jrs_attributes, by ="dsm") %>% 
  distinct() %>% 
  select(-`DSM Code`)->large_table
```
```{r}
emp_master %>% 
  select(c("dsm" = `DSM Code`,"title" = `DSM Code Title`, `EEO Job Category Title`)) %>% 
  mutate(dsm = as.numeric(dsm)) %>% 
  distinct()->emp_to_title
```

```{r}
read_csv("../data/jd_data_clean")->jd_clean

jd_clean %>% glimpse()
large_table %>% glimpse()

full_join(jd_clean, large_table, by="dsm") ->larger_table

larger_table %>%
  rename(c(job_summary=text_parsed2, supervisor_title = supervisor_title_sap)) %>%
  select(-supervisor_title_jrs) %>% 
  left_join(emp_to_title, by= "dsm") %>% 
  relocate(c(Title= title, dsm, Alternate_Title_jrs =`Job Title`,
             `Job Family`, supervisor_position, supervisor_dsm, supervisor_title, EEO=`EEO Job Category Title`))->last_table

last_table_2 <- last_table[sample(nrow(last_table)), ]

# Order rows such that NA values are at the bottom
df_ordered <- last_table_2[order(is.na(last_table_2$supervisor_title), last_table_2$supervisor_title), ]



# write.table(df_ordered, "../data/jdexpert.csv", sep = ",", quote = TRUE, row.names = FALSE, fileEncoding = "ISO-8859-1")

                         
```









